---
title: "README"
author: "U, Eisinger"
date: "4/17/2018"
output: html_document
---
#Project One README

###Getting Started
In order to begin this project, you must first pull a copy of all of the datafiles from GitHub onto your desktop as well as installing/calling any R libraries that will be used. This can be achieved through entering the code below into your terminal. 

####Prerequisites
The first step is to set the current directory to the desired location. The code below sets the current directory to your local desktop. This command will determine where the GitHub folder will end up. 
```{r cars}
##cd desktop    sets current directory to desktop
```
To Pull the data from GitHub and get it on your local desktop, use the command _git clone_ in the terminal. Copy the HTTPS from the GitHub repository that you wish to clone and paste in the terminal. 
```{r}
##git clone "https://github.com/ueisinger/ECONBD386"
```

####Installing 
The only library that is used is _dplyr_. You can call this library up using the following code. 
```{r}
##library(dplyr)
```


###Task One Materials 
The dataset included the following files. 
The files used in the dataframe for task one are listed below. 

Files | Purpose
------------ | -----------------------------
features.txt | A list of all of the features that were recorded for the experiment. This data is used as the columns for the dataframe. 
subject_train.txt | List of the subjects that partipated in this experiment.
subject_test.txt | List of the subjects that partipated in this experiment.
y_train.txt | List of the activity numeric values. 
y_test.txt | List of the activity numeric values. 
X_train.txt | List of the data obtained in the previous experiment. 
X_test.txt | List of the data obtained in the previous experiment. 

We also need the following files to gather more information about the datasets and the project as a whole.

Files | Purpose
------------ | -----------------------------
activity_labels.txt | Indicate the qualitative meausure of the activity data. These correspond to the numeric values in the y_train adn y_test dataset. 
features_info.txt | Description of each of the features and how exactlty they were obtained. 
README.txt | Overview of the original experiment and how the data was collected. 


###Task Two Materials
The file used for task two is below.

Files | Purpose
------------ | -----------------------------
Panel_8589.txt | Data obtained from the experiment _Decomposing Electric Power Plant Emmisions Within a Joint Production Framework_. 

We also need the following file to gather information about the dataset and the project as a whole. 

Files | Purpose
------------ | -----------------------------
Pasurka_2006.pdf | Research paper titled _Decomposing Electric Power Plant Emmisions Within a Joint Production Framework_. Includes Abstract, Introduction, Previous Research and References. 


